\subsection{Neuroevolution of augmenting topologies}
Neuroevolution uses evolutionary algorithms to optimise ANNs \cite{neuroevolution_review}.
One such algorithm is Neuroevolution of Augmenting Topologies (NEAT), which evolves the topology and weights of ANNs
using a genetic algorithm \cite{neat_main, neat_short, neat_phd}.

NEAT uses a direct encoding; genomes contain connection and node genes which specify the corresponding
network (see Figure \ref{mapping}). Each connection gene is identified by a number and
references the two nodes it connects. The node gene is also identified by a number.

\input{resources/tex/genotype_phenotype.tex}

The initial population of genomes encode structurally identical and fully connected networks without any hidden nodes.
New structures emerge through structural mutations which can add genes for new connections and nodes to the genomes.
Nodes are added by splitting an existing connection, which is then disabled and two new connection genes are added along
with the new node gene (see Figure \ref{node_mutation}).

\input{resources/tex/added_node_mutation.tex}

Mutations can also add new connections, which span any two previously unconnected nodes in the genome (see Figure \ref{link_mutation}).
Connections can be of three types, depending on their output node. Loops are connections that start and end on the same node. Recurrent
connections go backwards in the network to a node closer to an input node. Finally, forward connections end on a node closer to an output
node. The first two types of connections can provide a form of short term memory by repeating signals from a previous time step.

\input{resources/tex/added_link_mutation.tex}

The ID attribute of the genes, referred to as an innovation number, serves to uniquely identify each mutation that has occurred.
Each time a new link or node is added, a database containing all previous mutations and their IDs is referenced. That way,
identical links and nodes are labelled with the same ID.

NEAT protects new structures by placing similar networks in the population into species.
Competition mainly occurs within the species, ensuring that newly created structures are not prematurely deleted.
Since each gene is labelled with an ID, computing a measure of structural similarity is as simple as
comparing IDs in the genomes.

The IDs are also used during crossover to create meaningful offspring from networks with different structure.
They indicate the origin of each gene, making it possible to align link genes which span the same nodes in the genomes. Link genes
that are not present in either genomes are only inherited from the more fit parent. See Figure \ref{neat_overview} for an overview
of the NEAT algorithm.

\input{resources/tex/overview/overview.tex}
